Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-11-26 rnni_convexity.tex
update Fig2

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{RNNI}
\vspace{12pt}
\caption{Two types of operation that define edges of the $\rnni$ graph.
The rank move swaps the ranks of the two nodes in the tree on the left such that $\nni$ moves are possible on the edge between the two nodes marked by black dots.}
\label{fig:RNNI}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{RNNI}
\vspace{12pt}
\caption{Two types of operation that define edges of the $\rnni$ graph,
The rank move swaps the rank of the two highlighted nodes and the $\nni$ moves are performed on the blue edges.}
\label{fig:RNNI}
\end{figure}
